User-level Grid Monitoring with Inca 2

### 2007-02-26 pubs/papers/hpdc-gmw-2007/paper.tex
add future work section
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6558 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\SubSection{Inca administration tool (incat)}
%\begin{figure}[htb]
%  \centering
%  \mbox{\epsfig{file=incat.eps, width=\columnwidth}}
%  \caption{\label{arch_fig} Incat .}
%\end{figure}

@@

\SubSection{Graphing and Summary Statistics}

\SubSection{Knowledge Base}

\SubSection{Fault Tolerance}
~\newpage

>>>>

\SubSection{Inca administration tool (incat)}

\begin{figure*}[htb]
  \centering
  \mbox{\epsfig{file=incat.eps, width=\textwidth}}
  \caption{\label{arch_fig} Screenshot of incat that shows the reporters
  and their attributes available from the provided reporter repository.}
\end{figure*}

@@

In order to improve problem detection and diagnosis for system administrators,
we plan to enhance the data consumer with graph rendering and statistical
analysis capabilities.  This will improve troubleshooting capabilities by
allowing errors to be understood in a historical context.  It will also enable
summary displays analogous to those generated by Web page statistics packages
like Webalizer~\cite{webalizer} that provide a number of useful "Top"
statistics.  We expect feedback from TeraGrid and other Inca users on the
exact types of statistics and graphs that will prove to be most useful.  Our
goal is to offer a default set of statistics and graphs that can be used out
of the box and provide the capability to add others.

Also in order to make it easier for system administrators to troubleshoot
problems, we plan to enhance Inca with a knowledge base that can be used to
suggest solutions to problems (or point to known bugs if there is no solution
available).  The knowledge base would be populated by solutions provided by
system administrators, and the content would be self-moderated in order to
improve its quality (by voting or adding comments to each other's
contributions).  This knowledge base represents a potentially vital resource
for system administrators and provides a forum to share each other's
invaluable experience and skills.

Finally, we plan to improve the fault tolerance of Inca by enhancing the
reporter manager so that it caches reports locally if it is unable to
contact the depot or sends reports to a backup depot if one is available.
The agent will similarly be enhanced to cache configuration changes locally or
send configuration to a backup depot if one is available in case of a depot
failure.
